% resume.tex
% vim:set ft=tex spell:

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage{textcomp}
\usepackage{ebgaramond}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{-0.5#1}}%
    \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

\newcommand{\innerbullet}
{\hspace{0.6em}\textbullet\hspace{0.6em}}

% and the actual content starts here
\begin{document}

\begin{center}
    {\huge \textbf{Aaron Cunningham}}

    209.380.3039\innerbullet
    aa.cunningham@outlook.com\innerbullet
    Fresno, CA\\
    \href{https://github.com/aacunningham}{github.com/aacunningham}
\end{center}


\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
    \hyphenpenalty=1000
    \begin{description*}
        \item[Languages:]
            Python, Rust, SQL, TypeScript, JavaScript, HTML, CSS
        \item[Libraries/Frameworks:]
            Django, Django Rest Framework, pytest, tox, Actix Web, React, Angular, Vue
        \item[Technologies:]
            Git, Docker, Kubernetes, AWS, Linux, RDBMS, CI/CD (GitLab, GitHub Actions, Jenkins)
        \item[Other Skills:]
            Agile, Kanban, Scrum, Mob programming
    \end{description*}
\end{indentsection}


\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
    \parskip=0.1em

    \item
          \headerrow
          {\textbf{Senior Software Engineer}}
          {\textbf{2020 -- 2023}}
          \\
          \headerrow
          {\emph{Enervee}}
          {\emph{Venice, CA}}
          \begin{itemize*}
              \item Launched a financing integration for an ecommerce service, incorporating three Fintech integrations into a cohesive experience across a Django backend and AngularJS frontend.
              \item Led a team of four engineers in converting a regularly failing service to an event-based architecture, lowering the rate of errors requiring manual intervention to zero.
              \item Oversaw and maintained the API of a core internal service and it's VueJS microfrontend, communicating necessary changes and migration plans with other teams to meet a goal of zero downtime deployments.
              \item Coordinated with Product Managers to shape the roadmap of upcoming features, finding ways to incrementally reach goals and offering pragmatic trade-offs.
              \item Strengthened engineering skills of peers through regular code reviews and fostering an environment that encouraged sharing new ideas and solutions.
              \item Identified, diagnosed, and quickly resolved an issue spanning multiple codebases, implementing immediate actions to limit the impact and fully resolving the issue within one hour of detection.
          \end{itemize*}

    \item
          \headerrow
          {\textbf{Software Engineer}}
          {\textbf{2019 -- 2020}}
          \\
          \headerrow
          {\emph{Argon ST, a Boeing company}}
          {\emph{Fairfax, VA}}
          \begin{itemize*}
              \item Converted high level product specifications into an architectural design and a planned implementation schedule.
              \item Collaborated in a cross functional team of 3 engineers, focused on quick iterations, solicited user feedback, and used it to inform next goals for the project.
              \item Directed the development of a React/TypeScript frontend, trained new engineers unfamiliar with the technology, and guided more skilled engineers with relevant suggestions and best practices.
              \item Completed an eight month long project under budget and thirty days ahead of schedule.
          \end{itemize*}

    \item
          \headerrow
          {\textbf{Software Engineer}}
          {\textbf{2015 -- 2018}}
          \\
          \headerrow
          {\emph{Bixly}}
          {\emph{Fresno, CA}}
          \begin{itemize*}
              \item Communicated with clients and stakeholders regarding the status of projects and features, discussing potential roadblocks and alternative approaches to avoid them.
              \item Researched and estimated costs for planned feature work, providing clients with context to make informed decisions.
              \item Managed the full stack of multiple projects concurrently, approaching features and defects with a holistic view of the system.
          \end{itemize*}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
    \parskip=0.1em

    \item
          \headerrow
          {\textbf{College of Science and Mathematics, Computer Science, B.S.}}
          {\textbf{2010 -- 2016}}
          \\
          \headerrow
          {\emph{California State University, Fresno}}
          {\emph{Fresno, CA}}
          % \\
          % \headerrow
          % {\emph{College of Arts and Humanities, Music, Minor}}

\end{itemize}

\end{document}
